---
title: "Introduction to CounterfactMe"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to CounterfactMe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CounterfactMe)
```

# What CounterfactMe does

CounterfactMe generates random but plausible counterfactual Norwegian lives
from open data. Each call to `counterfact_me()` returns a coherent life:
name, age, education, occupation, income, family, housing, wealth, religion,
party preference, and a Bourdieu-style class profile.

```{r basic}
set.seed(1814)
counterfact_me(lang = "no")
```

# Conditional sampling

The package draws dimensions in a sociologically meaningful order. Age comes
first, then immigrant background, then name (drawn from origin region),
education, occupation, income, family structure, housing, wealth, identity
markers, and finally the Bourdieu profile.

# Selective dimensions

Pass a subset of dimensions if you only want certain fields:

```{r dims}
counterfact_me(dimensions = c("name", "age", "occupation"))
```

# Verifying consistency

For batch validation, `verify_consistency()` runs 22 cross-dimensional
checks across many draws and reports any inconsistencies.

```{r verify, eval=FALSE}
result <- verify_consistency(N = 1000)
result$summary
```

# Data sources

The packaged data is not uniformly traceable, and the package records
which parts are:

```{r sources, eval=FALSE}
data_sources()             # all 50 files
data_sources("untraced")   # those without a recorded origin
table(data_sources()$status)
```

Nine files are fetched from Statistics Norway's API by a script in
`data-raw/` and can be reproduced by running it again. Five cite an SSB
table in the R source but were transcribed by hand. Three are authored
content. The remaining 33 have neither a script nor a citation.

`untraced` does not mean invented: the figure may be an accurate
transcription of a published table. It means the origin has not been
established, which is work still to be done.
